Variation in use of East Asian Late Paleolithic weapons: A study of tip cross-sectional area of stemmed points from Korea

### 2022-10-26 analysis/paper/paper.qmd
Changed cords on shapefile
exploring GIS files and crs
made QGIS project

veg <- read_sf(here("analysis/data/gis_data/vegetation_polygons.shp"))

# take a look
ggplot() +
  geom_sf(data = veg)

@@

# Convert to class 'sf'
pts <- st_as_sf(korean_archaeological_site_locations_tcsa,
                coords = c( "long_dd", "lat_dd"),
                crs = st_crs(4326))

>>>>

veg <- read_sf(here("analysis/data/gis_data/Vegetation_polygon_2.shp"))

st_crs(veg)

# take a look
ggplot() +
  geom_sf(data = veg) +
  coord_sf()

@@

# Convert to class 'sf'
pts <- st_as_sf(korean_archaeological_site_locations_tcsa,
                coords = c( "long_dd", "lat_dd"),
                crs = st_crs(veg))
